---
title: "Summary of MB analysis"
author: "Ben Bond-Lamberty"
date: "March 22, 2014"
output: html_document
---

[//]: # Start by running the main analysis script (silently and cached)
```{r load_data, echo=FALSE, include=FALSE, cache=TRUE}
source( '3-bahn_analysis.R' )
```

```{r graphics_setup, include=FALSE, echo=FALSE}
library( ggplot2 )
theme_set( theme_bw() )
```

**Note**. This is my first R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see http://rmarkdown.rstudio.com.

**Abstract**

Summary of results:

* One result
* Another
* A third

### Introduction

### Methods

We examined studies in the soil respiration database (SRDB) which reported annual soil respiration (SR) as well as how instantaneous SR varied with temperature. 

Data were joined with global climate data set of air temperature, precipitation, and Palmer Drought Severity Index (PDSI).

Following Bahn et al. (2010) we estimated annual SR from SR at mean annual air temperature.

Data now include all studies published through 2012 (n=~`r nrow( srdb_orig )`).


### Results

**Dataset and climate coverage.** Depending on how tightly we constrain it, there are ~464 observations.

**Figure A.** Comparison of SRDB data (colored points) with global climate data set (grey background; darker squares mean more grid cells).

```{r figureA_climatefig, echo=FALSE, warning=FALSE}
figA   # prepared for us by 3-bahn_analysis.R, called above
```

**How well does the Bahn et al. (2010) equation predict annual SR?**

(All models fit after eliminating influential outliers, observations for which the temp-SR relationship didn’t encompass MAT, and observations where MAT diverged significantly from global climate data set.)

```{r mainmodelfit, echo=FALSE}
summary( m )    # prepared for us by 3-bahn_analysis.R, called above
intercept_test <- summary( m )$coefficients[ 1, 4 ]
slope_test <- summary( m1 )$coefficients[ 2, 4 ]
```

```{r mainmodelfit, echo=FALSE}
summary( m_05 )    # prepared for us by 3-bahn_analysis.R, called above
intercept_test <- summary( m_05 )$coefficients[ 1, 4 ]
slope_test <- summary( m1_05 )$coefficients[ 2, 4 ]
```
Answer: Need improve! Both models' slope close to 1, but differ from 1, intercept close to 0 but differ from 0. 
The relationship between predicted SR (via SR at MAT) and reported annual SR is 1:1, with a slope=1 (P=`r round( slope_test, 3 )`) and intercept=0 (P=`r round( intercept_test, 3 )`). There is significant unexplained variability, with R^2^=`r round( summary( m )$r.squared, 2 )` and RSE of `r round( summary( m )$sigma, 0 )` g C m^-2^ yr^-1^.

**Figure B.** Comparison between reported SR and SR inferred by Bahn et al. (2010) method. Dashed line is 1:1. Fitted solid line is surrounded by grey model error. Horizontal error bars show error (typically plot-to-plot), when reported by individual studies.
```{r figureB_prediction, echo=FALSE}
figB
```

**Is there a difference between heterotrophic- and autotrophic-dominated sites?**

Not many data (82 data points reporting SR as well as RH and RA), and no, there’s no statistical difference between these sites:

# TODO

**Figure C.** Difference between RA-dominated sites (RC_annual>0.5 is TRUE) and RH-dominated ones (RC_annual>0.5 is FALSE).

```{r figureC, echo=TRUE}'
                       
figC
```

**How does annual coverage affect the SR relationship?**

Studies report annual SR based on measurements that may span the entire year or, more frequently, less than a year (e.g. inferring annual SR from only growing season measurements). Unsurprisingly, more coverage means a better estimate of annual SR.

**Figure D.** Difference between low annual coverage (8-39% of year, red), medium coverage (39-69%, green), and high coverage (69-100%, blue).

```{r figureD, echo=FALSE}
#figD
```

**How much of the unexplained variability in Figure B is due to climate data set used?**

That is, studies in the SRDB were performed in specific locations whose climates might differ from the climate data set used. To quantify this effect we look at the difference between Tair in the climate data and mean annual air temperature during the study, which is (sporadically) reported in the database. About 10% of the data have air temperatures differing by >5 °C, and this does have a significant effect. 

**Figure E.** Effect of maximum allowed divergence between global climate data set and site-specific air temperature, when given. As we throw out data points with high divergence, R2 goes up (top panel) and RSE goes down (bottom, g C m-2 yr-1).
```{r figureE, echo=FALSE}
#figE
```

**Sites with more-variable air temperatures (across the year) exhibit worse fits.**

That is, the estimation of annual SR becomes poorer with greater variability in monthly air temperature.

**Figure F.** As **Figure B**, but broken into three groups by standard deviation of monthly air temperatures (°C). With higher variability, the regression significantly departs from 1:1.
```{r figureF, echo=FALSE}
#figF
```

**Sites with more-variable precipitation (across the year) exhibit worse fits.**

As with air temperature, the estimation of annual SR becomes poorer with greater variability in monthly precipitation.

**Figure G.** As **Figure B**, but broken into three groups by standard deviation of monthly precipitation (mm). With higher variability, the regression significantly departs from 1:1.

```{r figureG, echo=FALSE}
#figG
```

**Drought (as measured by max PDSI) had no significant effect.**

## TODO

**Figure H.** As **Figure B** but broken into three PDSI groups.
```{r figureH, echo=FALSE}
#figH
```


### Discussion

Other analyses?

### Software

This report was generated in RStudio (http://rstudio.com) using the following R packages:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
